%
% File: abstract.tex
% Author: V?ctor Bre?a-Medina
% Description: Contains the text for thesis abstract
%
% UoB guidelines:
%
% Each copy must include an abstract or summary of the dissertation in not
% more than 300 words, on one side of A4, which should be single-spaced in a
% font size in the range 10 to 12. If the dissertation is in a language other
% than English, an abstract in that language and an abstract in English must
% be included.

\chapter*{Abstract}
Kais NEFFATI, Computer Science Engineering , National Engineering School of Carthage Tunisia 
\newline
\newline
Abstract of a computer science engineer final year internship project , Submitted 29 Juin 2017 
\newline
\newline
Development and Design of a Community and social platform for Orange
\newline
\newline
\newline
\begin{SingleSpace}
\initial{T}he aim of this project is to design and develop a customized marketing system that allow Data analytics.
Today, This kind of systems are widely used. And have gained so much followers.
 This systems have successfully been one of the most powerful marketing strategies. 
 Today, the Orange group as a world wide company wants to implement one of this solutions. 
 For this reason the author (me) decided to commit to this project and consider it as it's graduation project.
This thesis first presents the host company, put the project in context and introduce the development, 
analysis and design methodologies. 
In a second stage, it introduce several technical and functional requirements specifications. 
Then it expose the system architectural and functional design.
Finally, we implement and expose our system features.

\end{SingleSpace}
\clearpage