%
% file: dedication.tex
% author: V?ctor Bre?a-Medina
% description: Contains the text for thesis dedication
%

\chapter*{Dedication and acknowledgements}
\begin{SingleSpace}
\initial{T}hroughout my life my family has always been there during those difficult and trying times. I would 
like to dedicate this thesis and everything I do to my father Noureddine NEFFATI, my mother Yosra REZGUI, my 
sister Chaima NEFFATI, my little sister Nesrine NEFFATI my brother-in-law Helmi CHEBBI and especially my nephew 
Zakaria CHEBBI.
Thanks to all my friends for sharing my happiness when starting this project and following with encouragement when it seemed too difficult to be completed. 
I would have probably given up without their support and example on what to do when you really want something.
At the end of this work, I would like to express my sincere thanks to all the people
Which have contributed, either directly or indirectly, to its smooth operation.
I would like to express my gratitude and sincere thanks to Mrs Ilhem ABDELHEDI,
My supervisor at Enicarthage, who knew with his professionalism and his pedagogical supervision
Guide me during these four months of training. I thank her for her regular follow-up
My advancement in the project, for his valuable advice and encouragement.
I would also like to thank my supervisors at Sofrecom Tunisia, Mr Walid HAMOUDA,
Development engineer, and Mr Mehdi KALAI, technical manager, for their availability,
Their advice and confidence.
I would also like to thank the entire Sofrecom Tunisia team for their hospitality, support and
Their team spirit.

\end{SingleSpace}
\clearpage